---
title: "Figures"
author: "Peterson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "figs/")
library(here)
library(tidyverse)
library(RColorBrewer)
library(ggpubr)
library(kableExtra)
```


```{r run_analysis, cache = TRUE, include = FALSE}
source(here("Code/analysis.R"))
```


# Figure 1

```{r fig1, fig.width=6.5, fig.height=10}

pal <- brewer.pal(4, "Blues")
pal[1] <- "tomato"
mar <- c(0, 18, 1, 1)
main_line <- -1

par(mar = mar, bg = "white", mfrow = c(4, 1))

## Stacked bar plot, best 5
pos_qual_df %>% 
  arrange(-mean_score) %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          legend.text = c("Not needed", "Useful, not critical", 
                          "Very important to have", "Absolutely must have"), 
          args.legend = list(horiz = TRUE, bty = "n", text.width=c(0.17, 0.25, 0.32, 0.3), x.intersp = .5),
          ylim = c(0,8.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("A: Most important positive traits", line = main_line-3.5, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

## Stacked bar plot, worst 5
pos_qual_df %>% 
  arrange(-mean_score) %>% 
  slice(16:20) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("B: Least important positive traits", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

## Stacked bar plot,Most agreed-upon (high consensus) positive traits
pos_qual_df %>% 
  arrange(sd_score) %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("C: Most agreed-upon positive traits", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = c(4, 0, 0, 0) + mar, bg = "white")

## Stacked bar plot, Most disagreed-upon (low consensus) positive traits
pos_qual_df %>% 
  arrange(sd_score) %>% 
  slice(16:20) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "") 
title("D: Least agreed-upon positive traits", line = main_line+.5, cex = 1.5, font.main = 1, adj = 0.5)
```

# Figure 2

```{r fig2, fig.width=6.5, fig.height=10}

pal <- brewer.pal(4, "Blues")
pal[1] <- "tomato"
mar <- c(0, 21, 1, 1)
main_line <- -1

par(mar = mar, bg = "white", mfrow = c(4, 1))

## Stacked bar plot, best 5
neg_qual_df %>% 
  arrange(-mean_score) %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          legend.text = c("Not problematic", "Consider avoiding DE", 
                          "Avoid DE if possible", "Avoid DE at all costs"), 
          args.legend = list(horiz = TRUE, bty = "n", text.width=c(0.26, .33, .33, 0.35), x.intersp = .5),
          ylim = c(0,8.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("A: Most important negative traits", line = main_line-3.5, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

## Stacked bar plot, worst 5
neg_qual_df %>% 
  arrange(-mean_score) %>% 
  slice(12:16) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("B: Least important negative traits", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

## Stacked bar plot,Most agreed-upon (high consensus) negative traits
neg_qual_df %>% 
  arrange(sd_score) %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("C: Most agreed-upon negative traits", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = c(4, 0, 0, 0) + mar, bg = "white")

## Stacked bar plot, Most disagreed-upon (low consensus) negative traits
neg_qual_df %>% 
  arrange(sd_score) %>% 
  slice(12:16) %>% 
  pivot_longer(cols = p_0:p_3, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "") 
title("D: Least agreed-upon negative traits", line = main_line+.5, cex = 1.5, font.main = 1, adj = 0.5)

```

# Figure 3

```{r fig3, fig.width=6.5, fig.height=10}

rf_qual_df <- rf_qual_df %>% 
  arrange(desc(mean_score))

pal <- c(rev(brewer.pal(3, "Reds")), brewer.pal(3, "Blues"))
pal <- pal[-4]

# Stacked bar plot, Most negatively perceived early signals
levs <- c("Definitely a bad sign", "Possibly a bad sign", "Indeterminate", 
          "Possibly a good sign", "Definitely a good sign")

mar <- c(0, 25, 1, 1)
main_line <- -1

par(mar = mar, bg = "white", mfrow = c(4, 1))

## Stacked bar plot, best 5
rf_qual_df %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_4, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          legend.text = levs, 
          args.legend = list(horiz = TRUE, bty = "n", 
                             text.width=c(0.3, 0.3, 0.2, 0.3, 0.3) + .02, 
                             x.intersp = .5),
          ylim = c(0,8.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("A: Most positively perceived early signals", line = main_line-3.5, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

## Stacked bar plot, worst 5
rf_qual_df %>% 
  slice(11:15) %>% 
  pivot_longer(cols = p_0:p_4, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("B: Most negatively perceived early signals", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = mar, bg = "white")

rf_qual_df %>% 
  arrange(sd_score) %>% 
  slice(5:1) %>% 
  pivot_longer(cols = p_0:p_4, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white",
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "", xaxt = "n") 
title("C: Most consensus", line = main_line, cex = 1.5, font.main = 1, adj = 0.5)

par(mar = c(4, 0, 0, 0) + mar, bg = "white")

rf_qual_df %>% 
  arrange(sd_score) %>% 
  slice(11:15) %>% 
  pivot_longer(cols = p_0:p_4, names_prefix = "p_") %>% 
  pivot_wider(id_cols = name, values_from = value, names_from = quality) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  barplot(horiz = TRUE, las = 2, col = pal, border = "white", 
          ylim = c(0,6.5), xlab = "Proportion of respondents",
          main = "") 
title("D: Least consensus", line = main_line+.5, cex = 1.5, font.main = 1, adj = 0.5)

```

# Figure 4: quality noteworthy associations

```{r fig4, fig.width=8.5, fig.height=12}
fig4A <- pretty_pos_fits %>% 
  # mutate(p = p.adjust(p, method = "fdr")) %>% 
  group_by(Quality) %>% 
  mutate(include = any(p<0.05)) %>% 
  ungroup() %>% 
  filter(include) %>% 
  mutate(sig = p < 0.05) %>% 
  ggplot(aes(x = Covariate, y = OR, col = sig + 1)) + 
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_segment(aes(y = ci_lb, yend = ci_ub, xend = Covariate)) + 
  facet_wrap(~Quality, nrow = 3, ncol = 2) + 
  scale_y_continuous(trans = "log", breaks = scales::log_breaks()) + 
  xlab("") + ylab("Odds ratio") +
  theme_pubr() +
  theme(legend.position = "none") 

fig4B <- pretty_neg_fits %>% 
  # mutate(p = p.adjust(p, method = "fdr")) %>% 
  group_by(Quality) %>% 
  mutate(include = any(p<0.05)) %>% 
  ungroup() %>% 
  filter(include) %>% 
  mutate(sig = p < 0.05) %>% 
  ggplot(aes(x = Covariate, y = OR, col = sig + 1)) + 
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_segment(aes(y = ci_lb, yend = ci_ub, xend = Covariate)) + 
  facet_wrap(~Quality) + 
  scale_y_continuous(trans = "log", breaks = scales::log_breaks()) + 
  xlab("") + ylab("Odds ratio") + 
  theme_pubr() +
  theme(legend.position = "none") 

ggarrange(fig4A, fig4B, ncol = 1, labels = c("A", "B"), heights = c(3/2, 1))

```

# Figure 5: Signal positivity noteworthy associations

```{r fig5, fig.width=8.5, fig.height=5}
pretty_rf_fits %>% 
  # mutate(p = p.adjust(p, method = "fdr")) %>% 
  group_by(Quality) %>% 
  mutate(include = any(p<0.05)) %>% 
  ungroup() %>% 
  filter(include) %>% 
  mutate(sig = p < 0.05) %>% 
  ggplot(aes(x = Covariate, y = OR, col = sig + 1)) + 
  geom_point() +
  geom_hline(yintercept = 1) +
  geom_segment(aes(y = ci_lb, yend = ci_ub, xend = Covariate)) + 
  facet_wrap(~Quality, ) + 
  scale_y_continuous(trans = "log", breaks = scales::log_breaks()) + 
  xlab("") + ylab("Odds ratio") + 
  theme_pubr() +
  theme(legend.position = "none") 

# Career support results
res_1 <- pos_fits$`DE supports your career goals`$Est
res_1_ci_lb <- pos_fits$`DE supports your career goals`$Est - 1.96 * pos_fits$`DE supports your career goals`$se
res_1_ci_ub <- pos_fits$`DE supports your career goals`$Est + 1.96 * pos_fits$`DE supports your career goals`$se

# big picture thinking results
res_2 <- pos_fits$`DE is good at big-picture thinking`$Est
res_2_ci_lb <- pos_fits$`DE is good at big-picture thinking`$Est - 1.96 * pos_fits$`DE is good at big-picture thinking`$se
res_2_ci_ub <- pos_fits$`DE is good at big-picture thinking`$Est + 1.96 * pos_fits$`DE is good at big-picture thinking`$se




```

# Supplemental figures

## Figure S1: Average reported importance of positive qualities

```{r figS1, fig.height=8, fig.width=11}
par(mar = c(5, 22, 0, 0))
pos_qual_df <- pos_qual_df %>% 
  arrange(mean_score)

plot(pos_qual_df$mean_score, 1:nrow(pos_qual_df), ylab = "", yaxt = "n", xlim = c(-.5,3.5), xlab = "", pch = 20, xaxt = "n", bty = "n") 
rect(-.5, 0, .5, 1+nrow(pos_qual_df), col = "tomato", border = FALSE)
rect(.5, 0, 1.5, 1+nrow(pos_qual_df), col = pal[2], border = FALSE)
rect(1.5, 0, 2.5, 1+nrow(pos_qual_df), col = pal[3], border = FALSE)
rect(2.5, 0, 3.5, 1+nrow(pos_qual_df), col = pal[4], border = FALSE)

points(pos_qual_df$mean_score, 1:nrow(pos_qual_df), pch = 20)
segments(
  x0 = pos_qual_df$mean_score - pos_qual_df$sd_score/sqrt(nrow(df)) * 1.96,
  x1 = pos_qual_df$mean_score + pos_qual_df$sd_score/sqrt(nrow(df)) * 1.96, 
  y0 = 1:nrow(pos_qual_df)
)
axis(2, at = 1:nrow(pos_qual_df), labels = pos_qual_df$quality, las = 1)
axis(1, at = 0:3, labels = c("Not needed", "Useful, not critical", "Very important", "Absolute must"))

```

## Figure S2: Average reported importance of negative qualities

```{r figS2, fig.height=8, fig.width=11}
par(mar = c(5, 24, 0, 0))
neg_qual_df <- neg_qual_df %>% 
  arrange(mean_score)

plot(neg_qual_df$mean_score, 1:nrow(neg_qual_df), ylab = "", yaxt = "n", xlim = c(-.5,3.5), xlab = "", pch = 20, xaxt = "n", bty = "n") 
rect(-.5, 0, .5, 1+nrow(neg_qual_df), col = "tomato", border = FALSE)
rect(.5, 0, 1.5, 1+nrow(neg_qual_df), col = pal[2], border = FALSE)
rect(1.5, 0, 2.5, 1+nrow(neg_qual_df), col = pal[3], border = FALSE)
rect(2.5, 0, 3.5, 1+nrow(neg_qual_df), col = pal[4], border = FALSE)

points(neg_qual_df$mean_score, 1:nrow(neg_qual_df), pch = 20)
segments(
  x0 = neg_qual_df$mean_score - neg_qual_df$sd_score/sqrt(nrow(df)) * 1.96,
  x1 = neg_qual_df$mean_score + neg_qual_df$sd_score/sqrt(nrow(df)) * 1.96, 
  y0 = 1:nrow(neg_qual_df)
)
axis(2, at = 1:nrow(neg_qual_df), labels = neg_qual_df$quality, las = 1)
axis(1, at = 0:3, labels = c("Not problematic", "Consider avoiding", "Avoid if possible", "Avoid at all costs"))
```

## Figure S3: Concordance of importance scores for positive qualities

```{r figS3, fig.height=8, fig.width = 10}
pos_qual_df2 <- df %>% 
  select(`DE is good at big-picture thinking`:`DE values team science`) %>% 
  sapply(function(x) {
    sd_ci <- misty::ci.sd(x, output = FALSE, method = "chisq")
    c(
      n_0 = sum(x == 0),
      n_1 = sum(x == 1),
      n_2 = sum(x == 2),
      n_3 = sum(x == 3),
      p_0 = mean(x == 0),
      p_1 = mean(x == 1),
      p_2 = mean(x == 2),
      p_3 = mean(x == 3),
      mean_score = mean(x),
      sd_score = sd(x),
      sd_lb = sd_ci$result$low,
      sd_ub = sd_ci$result$upp,
      coefvar_score = sd(x) / mean(x)
    )
  }) %>% 
  t() %>% as.data.frame()  %>% 
  rownames_to_column("quality") %>% 
  arrange(sd_score)
  
par(mar = c(5, 21, 4, 2))
plot(pos_qual_df2$sd_score, nrow(pos_qual_df2):1, ylab = "", yaxt = "n", 
     xlab = "SD(Score)", pch = 20, bty = "n", xlim = range(pos_qual_df2$sd_lb, pos_qual_df2$sd_ub)) 

segments(
  x0 = pos_qual_df2$sd_lb,
  x1 = pos_qual_df2$sd_ub, 
  y0 = nrow(pos_qual_df2):1,
)
axis(2, at = nrow(pos_qual_df2):1, labels = pos_qual_df2$quality, las = 1)
axis(1, at = c(.5, 1), labels = c("More consensus", "Less consensus"), las = 1, line = 2)
abline(v = c(1:10/10), col = "grey")

```


## Figure S4: Concordance of importance scores for negative qualities

```{r figS4, fig.height=8, fig.width = 10}
neg_qual_df2 <- df %>% 
  select(`DE is not productive`:`DE does not have a clear research plan or objective`) %>% 
  sapply(function(x) {
    sd_ci <- misty::ci.sd(x, output = FALSE, method = "chisq")
    c(
      n_0 = sum(x == 0),
      n_1 = sum(x == 1),
      n_2 = sum(x == 2),
      n_3 = sum(x == 3),
      p_0 = mean(x == 0),
      p_1 = mean(x == 1),
      p_2 = mean(x == 2),
      p_3 = mean(x == 3),
      mean_score = mean(x),
      sd_score = sd(x),
      sd_lb = sd_ci$result$low,
      sd_ub = sd_ci$result$upp,
      coefvar_score = sd(x) / mean(x)
    )
  }) %>% 
  t() %>% as.data.frame()  %>% 
  rownames_to_column("quality") %>% 
  arrange(sd_score)

par(mar = c(5, 23, 4, 3))
plot(neg_qual_df2$sd_score, nrow(neg_qual_df2):1, ylab = "", yaxt = "n", 
     xlab = "SD(Score)", pch = 20, bty = "n", xlim = range(neg_qual_df2$sd_lb, neg_qual_df2$sd_ub)) 

segments(
  x0 = neg_qual_df2$sd_lb,
  x1 = neg_qual_df2$sd_ub, 
  y0 = nrow(neg_qual_df2):1,
)
axis(2, at = nrow(neg_qual_df):1, labels = neg_qual_df$quality, las = 1)
axis(1, at = c(.4, 1.2), labels = c("More consensus", "Less consensus"), las = 1, line = 2)
abline(v = c(1:10/5), col = "grey")

```

## Figure S5: Average reported positivity of early signals

```{r figS5, fig.height=8, fig.width = 10}

rf_qual_df <- rf_qual_df %>% 
  arrange(mean_score)

par(mar = c(5, 25, 4, 1))
plot.new()
plot(rf_qual_df$mean_score, 1:nrow(rf_qual_df), ylab = "", yaxt = "n", xlim = c(-.5,4.5), 
     xlab = "", pch = 20, xaxt = "n", bty = "n") 
rect(-.5, 0, .5, 1+nrow(rf_qual_df), col = pal[1], border = FALSE)
rect(.5, 0, 1.5, 1+nrow(rf_qual_df), col = pal[2], border = FALSE)
rect(1.5, 0, 2.5, 1+nrow(rf_qual_df), col = pal[3], border = FALSE)
rect(2.5, 0, 3.5, 1+nrow(rf_qual_df), col = pal[4], border = FALSE)
rect(3.5, 0, 4.5, 1+nrow(rf_qual_df), col = pal[5], border = FALSE)

points(rf_qual_df$mean_score, 1:nrow(rf_qual_df), pch = 20)
segments(
  x0 = rf_qual_df$mean_score - rf_qual_df$sd_score/sqrt(nrow(df)) * 1.96,
  x1 = rf_qual_df$mean_score + rf_qual_df$sd_score/sqrt(nrow(df)) * 1.96, 
  y0 = 1:nrow(rf_qual_df)
)
axis(2, at = 1:nrow(rf_qual_df), labels = rf_qual_df$quality, las = 1)
axis(1, at = c(0, 2, 4), labels = c("Definitely a bad sign", 
                             "Indeterminate", "Definitely a good sign"))

```

## Figure S6: Concordance of early signal positivity

```{r figS6, fig.height=8, fig.width = 10}
rf_qual_df2 <- df %>% 
  select(`Your peer tells you they had a bad experience with the DE`:`The DE dismisses opinions of others on the team`,
         `Your gut tells you the DE will be good to work with`) %>% 
  sapply(function(x) {
    sd_ci <- misty::ci.sd(x, output = FALSE, method = "chisq")
    c(
      n_0 = sum(x == 0),
      n_1 = sum(x == 1),
      n_2 = sum(x == 2),
      n_3 = sum(x == 3),
      n_4 = sum(x == 4),
      p_0 = mean(x == 0),
      p_1 = mean(x == 1),
      p_2 = mean(x == 2),
      p_3 = mean(x == 3),
      p_4 = mean(x == 4),
      mean_score = mean(x),
      sd_score = sd(x),
      sd_lb = sd_ci$result$low,
      sd_ub = sd_ci$result$upp
    )
  }) %>% 
  t() %>% as.data.frame()  %>% 
  rownames_to_column("quality") %>% 
  arrange(sd_score)
  
par(mar = c(5, 25, 4, 1))
plot.new()
plot(rf_qual_df2$sd_score, nrow(rf_qual_df2):1, ylab = "", yaxt = "n", 
     xlab = "SD(Score)", pch = 20, bty = "n", xlim = range(rf_qual_df2$sd_lb, rf_qual_df2$sd_ub)) 

points(rf_qual_df2$sd_score, nrow(rf_qual_df2):1, pch = 20)
segments(
  x0 = rf_qual_df2$sd_lb,
  x1 = rf_qual_df2$sd_ub, 
  y0 = nrow(rf_qual_df2):1
)
axis(2, at = nrow(rf_qual_df2):1, labels = rf_qual_df2$quality, las = 1)
axis(1, at = c(.5, 1), labels = c("More consensus", "Less consensus"), las = 1, line = 2)
abline(v = c(1:20/10), col = "grey")
```

# Supplemental tables 

## Table S1: Likert response tabulation for all positive characteristics

```{r tabS1}
pos_qual_df %>% 
  arrange(desc(mean_score)) %>% 
  mutate("Not needed" = paste0(n_0, " (", round(100*p_0, 1), "%)"),
         "Useful to have, not critical" = paste0(n_1, " (", round(100*p_1, 1), "%)"),
         "Very important to have" = paste0(n_2, " (", round(100*p_2, 1), "%)"),
         "Absolutely must have" = paste0(n_3, " (", round(100*p_3, 1), "%)"),
         ) %>% 
  select(-n_0:-coefvar_score, Quality = quality) %>% 
  kable(align = "lcccc") %>% 
  kable_styling(c("condensed", "striped"), full_width = FALSE) %>% 
  column_spec(1, width = c("11cm")) %>% 
  column_spec(2:5, width = c("2.5cm"))
```

## Table S2: Likert response tabulation for all negative characteristics

```{r tabS2}
neg_qual_df %>% 
  arrange(desc(mean_score)) %>% 
  mutate("Not problematic" = paste0(n_0, " (", round(100*p_0, 1), "%)"),
         "Consider avoiding DE" = paste0(n_1, " (", round(100*p_1, 1), "%)"),
         "Avoid DE if possible" = paste0(n_2, " (", round(100*p_2, 1), "%)"),
         "Avoid DE at all costs" = paste0(n_3, " (", round(100*p_3, 1), "%)"),
         ) %>% 
  select(-n_0:-coefvar_score, Quality = quality) %>% 
  kable(align = "lcccc") %>% 
  kable_styling(c("condensed", "striped"), full_width = FALSE) %>% 
  column_spec(1, width = c("11cm")) %>% 
  column_spec(2:5, width = c("2.5cm"))
```

## Table S3: Likert response tabulation for all early signals

```{r}
rf_qual_df %>% 
  arrange(desc(mean_score)) %>% 
  mutate("Definitely a bad sign" = paste0(n_0, " (", round(100*p_0, 1), "%)"),
         "Possibly a bad sign" = paste0(n_1, " (", round(100*p_1, 1), "%)"),
         "Indeterminate" = paste0(n_2, " (", round(100*p_2, 1), "%)"),
         "Possibly a good sign" = paste0(n_3, " (", round(100*p_3, 1), "%)"),
         "Definitely a good sign" = paste0(n_4, " (", round(100*p_4, 1), "%)"),
         ) %>% 
  select(-n_0:-coefvar_score, Quality = quality) %>% 
  kable(align = "lccccc") %>% 
  kable_styling(c("condensed", "striped"), full_width = FALSE) %>% 
  column_spec(1, width = c("11cm")) %>% 
  column_spec(2:6, width = c("2.5cm"))

```


## Table S4: All associations from ordinal regression models for positive qualities

```{r tabS4}
# Positive quality associations table
idx <- rep(3, length(pos_fits))
names(idx) <- names(pos_fits)

pretty_pos_fits %>% 
  select(Covariate, OR, ci_lb, ci_ub, p) %>%
  mutate(p = CIDAtools::pvalr(p)) %>% 
  kable(digits = 2, row.names = F) %>% 
  kable_minimal(full_width = FALSE) %>% 
  group_rows(index = idx)

```

## Tables S5: All associations from ordinal regression models for negative qualities

```{r tabS5}
# Negative quality associations table
idx <- rep(3, length(neg_fits))
names(idx) <- names(neg_fits)

pretty_neg_fits %>% 
  select(Covariate, OR, ci_lb, ci_ub, p) %>%
  mutate(p = CIDAtools::pvalr(p)) %>% 
  kable(digits = 2, row.names = F) %>% 
  kable_minimal(full_width = FALSE) %>% 
  group_rows(index = idx)

```


## Tables S6: All associations from ordinal regression models for early signals

```{r tabS6}
# Early signal associations table
idx <- rep(3, length(rf_fits))
names(idx) <- names(rf_fits)

pretty_rf_fits %>% 
  select(Covariate, OR, ci_lb, ci_ub, p) %>%
  mutate(p = CIDAtools::pvalr(p)) %>% 
  kable(digits = 2, row.names = F) %>% 
  kable_minimal(full_width = FALSE) %>% 
  group_rows(index = idx)
```

